---
title: "Pushups Problem"
output:
  html_document:
    highlight: monochrome
    toc: true
    df_print: paged
date: '`r format(Sys.time(), "%d %B, %Y")`'
author: 'Logan Martinez'
---

```{r include=FALSE,echo=FALSE}

require(tidyverse)
require(tigerstats)

```

# Introduction 

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?

Fork the Rstudio project called pushups to your github account. Clone from your github account to your Rstudio.cloud CRN37591 workspace.  Using the dataset called pushups from the tigerstats package in R, answer the question posed by this null and alternate hypothesis in an html markdown document. -->

$H_0$: There is no difference between the average number of pushups done in two minutes between line and skill players

$H_A$: There is a difference between the  average number of pushups done in two minutes between line and skill players.

Commit the .rmd and .html file, push to your github accout, submit  the URL once you've completed the assignment

<!-- load the data set -->

```{r}
players <- pushups
```


Two football players at GC asked their team-mates to do as many pushups as they could in two minutes.


A data frame with 30 observations on the following 3 variables.

**_weight_**  
weight of subject in pounds.

**_pushups_**  
number of pushups the player completed in two minutes.

**_position_**  
a factor with levels **LINE**, **SKILL**: type of position played by the subject. Line positions require high body mass, skill positions require a lot of running around- run the 40 yd dash in under 4.4 sec 

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.  
  
Variable analysis: You have position (factor) and number of pushups done in two minutes (numerical). What type of graphical display, numerical display and inferential test is appropriate?  

position is categorical, pushups is numerical. so we use numerical ~ categorical 
graphical: boxplot
summary: data summary
inference: t-test to compare means

# Descriptive Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->



### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question

Typically look at boxplots when considering numerical vs categorical data. Insert a boxplot here

The two variables of interest are pushups and position. Boxplot graphical displays are good ways to depict data.  --> 

```{r}
plot(pushups~position, data=players)
```
  
  The box plot for the skilled players is contained within more pushups done when compared to the line players. Skilled gravitates towards the 50's whereas line gravitates towards the 15's.
  
<!-- be sire to tell what the boxplot shows -->
 
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question -->

```{r}
summary(players)
```

Based on the summary, the skill contains 22 whereas the line contains 8, meaning that more pushups were done by skill players versus the line players.

# Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question -->


```{r}
t.test(pushups~position, data=players)
```

this t-test shows that the mean between the line and skilled players is quantifiable. Not only that, but the p-value is below 0.05.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. -->

the t-test to compare means, has a p-value of 0.0000009421
this is less than 0.05, therefore we reject the null hypothesis, and conclude that we have evidencethat there is a difference in the average number of pushups that can be done in 2 minutes by line and skill players.
